Frozen Civil Conflicts

### 2024-01-29 paper.qmd
Add sbc histograms

```{r}
filter(dataset, frozen == 1) |>
    arrange(side_a, year) |>
    select(Government = side_a, `Rebel Group(s)` = side_b, Year = year) |>
    mutate(Government = sub("Government of", "", Government) |> trimws()) |>
    kable(longtable = T)
```

@@

>>>>

```{r}

filter(dataset, frozen == 1) |>
    arrange(side_a, year) |>
    select(Government = side_a, `Rebel Group(s)` = side_b, Year = year) |>
    mutate(Government = sub("Government of", "", Government) |> trimws()) |>
    kable(longtable = T)
```

@@

```{R}
sbc <- readRDS("./posteriors/sbc.rds") |>
    select(-.chain, -.iteration, -.draw) |>
    pivot_longer(everything())

ggplot(sbc, aes(x = value)) +
    geom_histogram(bins = 10) +
    facet_wrap(~ name, scales = "free") +
    theme(axis.title.y = element_blank(),
          axis.title.x = element_blank())
```
